\huge Tor's Usability for Censorship Circumvention

### 2016-05-12 pets2017-paper/pets2017-paper.tex
anonymize.

\begin{document}

  \author*[1]{Linda Lee}

  \author[2]{David Fifield}

  \author[3]{Nathan Malkin}

  \author[4]{Ganesh Iyer}

  \author[5]{Serge Egelman}

  \author[6]{David Wagner}

  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}

  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

@@

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability in this role.
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative user study tests the impact of our changes.
We find that our changes result in a significant reduction 
in the time spent configuring a connections. We
conclude with recommendations for changes to the current interface as well as 
alternative approaches to bootstrapping a connection to Tor.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\subsection{Setup}
We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using Xlab.

@@

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.

\subsection{Procedure}
The one-hour, multi-participant procedure began when all participants sat at their
respective computers in Xlab. Each computer was equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to a simulated censorship environment combination at random.

@@

\section{Limitations} 
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at Xlab. Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

\section {Resources} 
For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\

\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}

\section {Acknowledgments}
I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

@@

\section{Qualitative User Study Recruitment Posting} 
\label{qualitative-recruitment}
We are recruiting participants for an in-person research study at the University of California, Berkeley. You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.

\section{Qualitative User Study Prescreening Survey} 
\label{qualitative-prescreening}
We are recruiting participants for an in-person research study at the University of California, Berkeley. You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\

\begin{enumerate}
\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
\item{I am able to provide my own transportation to the University of California, Berkeley campus.}
\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
\item{What is your gender?}
\item{What is your age?}
\item{Please select your highest completed (or current) level of education.}
\item{What is your occupation?} 
\item{Do you speak any languages other than English fluently?}
\item{If you have a personal computer, what kind do you use?}
\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
\item{How often do you use the following software or features? \textit{<answer choices: a grid of radio buttons. Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption. Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
\end{enumerate}
Thank you for filling out this form. You are now done!

@@

\section{Quantitative User Recruitment Posting}
\label{quantitative-recruitment}
We are recruiting up to 40 participants for a user study at UC Berkeley. The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\

\indent Payment: \$30 Amazon gift card\\
\indent Duration: 1 hour \\
\indent Where: Xlab at Hearst Memorial Gymnasium\\

@@

If you are interested: 1. Email lnl@berkeley.edu with the sessions you are able to attend. We will confirm your participation and assign you a session. 2. Come to Xlab at the appointed time for the experiment.

@@

This survey is part of a research project being conducted by the University of California, Berkeley. If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's Committee for Protection of Human Subjects at 510-642-7461, or email subjects@berkeley.edu. If you agree to participate, please click Next below.\\

@@

\section{Custom Bridge Attempts} 
\label{custom}

@@

\section{All Participant Times}
\label{all-participant-times}
Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface. These are the raw numbers used to compute values such as the median time spend on each screen.   Participants are grouped by condition. Within each condition, participants are ordered in the order of time to success. For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.

\begin{table*}
\input{all-participant-times.tex}
\caption{
Times spent on each screen, per participant.
}
\label{table:all-participant-times}
\end{table*}

@@

Participants that downloaded Tor Browser (5/124): 
\begin{itemize}
\item P115 (Fig.~\ref{softsonic})
\item P116 (Fig.~\ref{techspot})
\item P117, data not used (Fig.~\ref{mirror})
\item P118, data not used (Fig.~\ref{downloadio})
\item P119, data not used (Fig.~\ref{driverupdate})
\end{itemize}

>>>>

\begin{document}
   \author*[1]{Author 1}

  \author[2]{Author 2}

  \author[3]{Author 3}

  \author[4]{Author 4}

  \author[5]{Author 5}

  \author[6]{Author 6}

  \affil[1]{Affiliation of Author 1, E-mail: \mbox{author1@affiliation.edu}}
  \affil[2]{Affiliation of Author 2, E-mail: \mbox{author2@affiliation.edu}}
  \affil[3]{Affiliation of Author 3, E-mail: \mbox{author3@affiliation.edu}}
  \affil[4]{Affiliation of Author 4, E-mail: \mbox{author4@affiliation.edu}}
  \affil[5]{Affiliation of Author 5, E-mail: \mbox{author5@affiliation.edu}}
  \affil[6]{Affiliation of Author 6, E-mail: \mbox{author6@affiliation.edu}}
%  \author*[1]{Linda Lee}
%
%  \author[2]{David Fifield}
%
%  \author[3]{Nathan Malkin}
%
%  \author[4]{Ganesh Iyer}
%
%  \author[5]{Serge Egelman}
%  
%  \author[6]{David Wagner}
%
%  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
%
%  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
%
%  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
%
%  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
%  
%  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
%   
%  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

@@

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability in this role.
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative user study tests the impact of our changes.
We find that our changes result in a significant reduction 
in the time spent configuring a connections. We
conclude with recommendations for changes to the current interface as well as 
alternative approaches to bootstrapping a connection to Tor.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\subsection{Setup}
We ran our experiment at <redacted> 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
<redacted> %Xlab 
has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.

@@

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the <redacted> %Xlab 
participant pool. Although <redacted> %Xlab 
participants are not limited to <redacted> %UC Berkeley 
students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.

\subsection{Procedure}
The one-hour, multi-participant procedure began when all participants sat at their
respective computers in <redacted>. %Xlab. 
Each computer was equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to a simulated censorship environment combination at random.

@@

\section{Limitations} 
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab. 
Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

%\section {Resources} 
%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
%
%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
%
%\section {Acknowledgments}
%I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

@@

\section{Qualitative User Study Recruitment Posting} 
\label{qualitative-recruitment}
We are recruiting participants for an in-person research study at <redacted>. %the University of California, Berkeley. 
You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.

\section{Qualitative User Study Prescreening Survey} 
\label{qualitative-prescreening}
We are recruiting participants for an in-person research study at the <redacted>. %University of California, Berkeley. 
You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\

\begin{enumerate}
\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
\item{I am able to provide my own transportation to the <redacted> %University of California, Berkeley 
campus.}
\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
\item{What is your gender?}
\item{What is your age?}
\item{Please select your highest completed (or current) level of education.}
\item{What is your occupation?} 
\item{Do you speak any languages other than English fluently?}
\item{If you have a personal computer, what kind do you use?}
\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
\item{How often do you use the following software or features? \textit{<answer choices: a grid of radio buttons. Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption. Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
\end{enumerate}
Thank you for filling out this form. You are now done!

@@

\section{Quantitative User Recruitment Posting}
\label{quantitative-recruitment}
We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\

\indent Payment: \$30 Amazon gift card\\
\indent Duration: 1 hour \\
\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\

@@

If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
with the sessions you are able to attend. We will confirm your participation and assign you a session. 
2. Come to <redacted> %Xlab 
at the appointed time for the experiment.

@@

This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
Committee for Protection of Human Subjects at 510-642-7461, or email 
<redacted>. %subjects@berkeley.edu. 
If you agree to participate, please click Next below.\\

@@

\section{Custom Bridge Attempts} 
We provide screenshots of the messages sent to the bridges autoresponder. 
\label{custom}

@@

%\section{All Participant Times}
%\label{all-participant-times}
%Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface. These are the raw numbers used to compute values such as the median time spend on each screen.   Participants are grouped by condition. Within each condition, participants are ordered in the order of time to success. For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.  
%
%\begin{table*}
%\input{all-participant-times.tex}
%\caption{
%Times spent on each screen, per participant.
%}
%\label{table:all-participant-times}
%\end{table*}

@@

5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softsonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).
